---
title: "HPCC"
author: "nikolays"
date: "11/30/20"
output:
  html_document:
    toc: yes
    toc_depth: '3'
    df_print: paged
  html_notebook:
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(cowplot)
library(knitr)
library(kableExtra)
```

```{r include=FALSE}
# Read data
load("hpcc.Rdata")
hpcc_nov <- filter(hpcc,cores == 48L)
hpcc_nov$config <- paste0(hpcc_nov$config,"; Nov")
hpcc_nov$resource <- "Ookami"
hpcc_nov$nodes <- NULL

hpcc_oct <- rbind(
    read.csv("../../koinu/data/hpcc.csv", stringsAsFactors=F),
    read.csv("../data/hpcc.csv", stringsAsFactors=F))
hpcc_oct$X <- NULL
hpcc_oct$problem_size <- NULL
hpcc_oct$nodes <- NULL
hpcc_oct$value <- as.numeric(hpcc_oct$value)
hpcc_oct <- hpcc_oct %>% filter(!is.na(value))
hpcc_oct <- hpcc_oct %>% rename(config=exe_type,id=run_id,cores=cpus)
hpcc_oct <- hpcc_oct %>% filter(resource!="Stampede2 SKX (CPU Intel Xeon Platinum 8160 24(48) cores x2)")
hpcc_oct <- hpcc_oct %>% filter(!(resource=="Koinu (CPU ARM ThunderX2 32(128) cores x2)" & cores!=64))

hpcc_oct$config <- paste0(hpcc_oct$resource, "; ",hpcc_oct$config)

m <- hpcc_oct$resource=="Ookami"
hpcc_oct$config[m] <- paste0(hpcc_oct$config[m],"; Oct")


hpcc <- rbind(
  hpcc_oct,
  hpcc_nov
)
unique(paste0(as.character(hpcc_nov$config[m]),"; Oct"))
colnames(hpcc_nov)
colnames(hpcc_oct)
unique(hpcc_oct$resource)
```



```{r include=FALSE}
# statistics we are interested in
#dput(unique(hpcc$metric[hpcc$metric_type=="statistic"]))
stats_overall <- c(
    "High Performance LINPACK Floating-Point Performance",
    "Fast Fourier Transform (FFTW) Floating-Point Performance",
    "Parallel Matrix Transpose (PTRANS)",
    "MPI Random Access"
)
stats_per_core <- c(
    "Average Double-Precision General Matrix Multiplication (DGEMM) Floating-Point Performance",
    "Average STREAM 'Triad' Memory Bandwidth",
    "Average STREAM 'Add' Memory Bandwidth",
    "Average STREAM 'Copy' Memory Bandwidth",
    "Average STREAM 'Scale' Memory Bandwidth"
)
units <- hpcc %>% group_by(metric) %>% summarise(units=as.character(first(units)),.groups = "drop_last") %>%
    ungroup()
units$units[is.na(units$units)]<-""
```

Everything is executed on single node, average of 10 runs.

# Metrics

Some of reported HPCC metrics:

 * Average Double-Precision General Matrix Multiplication (DGEMM) Floating-Point Performance
   + Embarrassingly parallel, Averaged over all MPI process, MFLOP per Second per MPI process
   + (There is also serial metric; measured but not analysed)
 * High Performance LINPACK Floating-Point Performance
   + Parallel, overall MFLOP per Second
 * Fast Fourier Transform (FFTW) Floating-Point Performance
   + Parallel, MFLOP per Second
   + (There are also serial and embarrassingly parallel metrics; measured but not analysed)
 * Parallel Matrix Transpose (PTRANS)
   + Parallel, overall MByte per Second
 * MPI Random Access
   + Parallel, overall MUpdate per Second
   + (There are also serial and embarrassingly parallel metrics; measured but not analysed)
 * Average STREAM 'Triad'/ 'Add' / 'Copy' / 'Scale' Memory Bandwidth
   + Embarrassingly parallel, Averaged over all MPI process, MByte per Second
   + (There is also serial metric; measured but not analysed)

# Results
## Selected metrics

### DGEMM
```{r results='asis', echo=FALSE, fig.width = 6.4, fig.height = 8}

# Averaged over all MPI process
# so report per core
s_dgemm <- "Average Double-Precision General Matrix Multiplication (DGEMM) Floating-Point Performance"
dgemm <- hpcc %>% filter(metric == s_dgemm) %>%
        group_by(config) %>%
        summarise(average=mean(value),stdev=sd(value),.groups = "drop_last") %>%
        ungroup()
#dput(unique(dgemm$config))

dgemm$average <- dgemm$average / 1000
dgemm$stdev <- dgemm$stdev / 1000
dgemm$tflops <- 57.6
dgemm$tflops[grepl("Stampede2-SKX",dgemm$config)] <- 44.8
dgemm$tflops[!(grepl("Stampede2-SKX",dgemm$config) | grepl("Ookami",dgemm$config))] <- NA

dgemm <- dgemm %>% filter(config != "Koinu (CPU ARM ThunderX2 32(128) cores x2); openmpi/sysblas/intfft") %>% 
  filter(config != "Ookami; mvapich2/libsci/intfft/cce; Oct")

dgemm$label <- paste0(round(dgemm$average,1),if_else(is.na(dgemm$tflops),"", paste0(" (",round(100*dgemm$average/dgemm$tflops,1),"%)")))
# ookami: single core peak (57.6 GFLOP/s)
# stampede avx512 base 1.4 GHz turbo 2.0
# https://www.intel.com/content/dam/www/public/us/en/documents/specification-updates/xeon-scalable-spec-update.pdf
# freq*8(width)*2*(fma)*2(units)
# stampede peak=44.8 (64 at turbo)

LArename <- list(
  "Ookami; openmpi/armpl/armpl/gcc; Oct"="Ookami, ARMPL (Early Oct)",
  "Ookami; mvapich/armpl/armpl/armc; Oct"="Ookami, ARMPL (Oct)",
  "Ookami; mvapich2/libsci/fftw3/cce; Oct"="Ookami, LibSci (Oct)",
  
  "Ookami; gcc,armpl,mvapich; Nov"="Ookami, ARMPL (Nov)", 
  "Ookami; cray,libsci,fftw-cray,mvapich; Nov"="Ookami, LibSci (Nov)", 
  "Ookami; gcc,openblas,fftw-rd,mvapich; Nov"="Ookami, OpenBLAS (Nov)",
  
  "Koinu (CPU ARM ThunderX2 32(128) cores x2); openmpi/armpl/intfft"="Koinu (ARM ThunderX2), ARMPL", 
  "Koinu (CPU ARM ThunderX2 32(128) cores x2); openmpi/openblas/intfft"="Koinu (ARM ThunderX2), OpenBLAS", 
  
  "Stampede2-SKX; icc,mkl,intel-mpi; Nov"="Stampede2 (Skylake-X), MKL",
  "Stampede2 KNL (CPU Intel Xeon Phi 7250 68(272) cores x2); impi/mkl"="Stampede2 (Knights Landing), MKL",
  
  "Bridges (Intel E5-2695 v3 14 cores x2, Haswell); impi/mkl"="Bridges (Haswell), MKL", 
  "Comet (CPU Intel Xeon E5-2680v3 12 cores x2, Haswell); mvapich2/mkl"="Comet (Haswell), MKL"
)
dgemm$config <- recode(dgemm$config,!!!LArename)
LAorder <- LArename
names(LAorder) <- NULL
dgemm$config <- factor(dgemm$config,levels = rev(LAorder))

dgemm$color2 <- "purple"
dgemm$color2[grepl("Oct",dgemm$config)] <- "greenyellow"
dgemm$color2[grepl("Nov",dgemm$config)] <- "royalblue"
dgemm$color2[grepl("MKL",dgemm$config)] <- "skyblue"
dgemm$color2[grepl("Skylake-X",dgemm$config)] <- "royalblue1"

ggplot(dgemm, aes(x=config, y=average)) +
        geom_bar(stat="identity", fill=dgemm$color2, color="black") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
  geom_text(aes(label=label),hjust=-.2, vjust=0.5)+
        ylab("Matrix Multiplication (DGEMM), GFLOP/s per core")+
        coord_flip()+ ylim(0,65)+
  theme(axis.title.y=element_blank(),
        axis.text.y = element_text(color="black",size=12))

```

### HPL
```{r results='asis', echo=FALSE, fig.width = 6, fig.height = 2}

# Averaged over all MPI process
# so report per core
s_hpl <- "High Performance LINPACK Floating-Point Performance"
hpl <- hpcc %>% filter(metric == s_hpl) %>%
        group_by(config,cores) %>%
        summarise(average=mean(value),stdev=sd(value),.groups = "drop_last") %>%
        ungroup()

hpl$config <- recode(hpl$config,!!!LArename)
hpl$config <- factor(hpl$config,levels = rev(c("Ookami, LibSci","Ookami, ARMPL","Ookami, OpenBLAS","Stampede2-SKX, MKL")))
hpl$nodes <- as.integer(hpl$cores/48)
hpl$average <- hpl$average / 1000
hpl$stdev <- hpl$stdev / 1000
hpl$tflops <- 57.6 * hpl$cores
hpl$tflops[grepl("Stampede2",hpl$config)] <- 44.8 * hpl$cores
hpl$label <- paste0(round(hpl$average,0)," (",
                      round(100*hpl$average/hpl$tflops,1),"%)")
# ookami: single core peak (57.6 GFLOP/s)
# stampede avx512 base 1.4 GHz turbo 2.0
# https://www.intel.com/content/dam/www/public/us/en/documents/specification-updates/xeon-scalable-spec-update.pdf
# freq*8(width)*2*(fma)*2(units)
# stampede peak=44.8 (64 at turbo)


ggplot(hpl %>% filter(nodes==1), aes(x=config, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
  geom_text(aes(label=label),hjust=-.15, vjust=0.5)+
        ylab("High Performance LINPACK, GFLOP/s per node")+
        coord_flip()+ ylim(0,1500)+
  theme(axis.title.y=element_blank(),
        axis.text.y = element_text(color="black",size=12))
```

```{r results='asis', echo=FALSE, fig.width = 4, fig.height = 4}
hpl_perf <- read.csv("perfect_scaling.csv",sep=";",as.is = T)
hpl$sys <- factor(as.character(hpl$config),levels = c("Ookami, LibSci","Ookami, ARMPL","Ookami, OpenBLAS","Stampede2-SKX, MKL"))
hpl_perf$sys <- factor(as.character(hpl_perf$config),levels = c("Ookami, LibSci","Ookami, ARMPL","Ookami, OpenBLAS","Stampede2-SKX, MKL"))

ggplot(hpl, aes(x=nodes, y=average, color=sys)) + geom_point() + geom_line() +
  geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=0.05) + labs(color="") +
  geom_line(data = hpl_perf,mapping = aes(x=nodes, y=average, color=sys), linetype = 2) +
  scale_x_continuous(trans='log2') +
  scale_y_continuous(trans='log10') +
  ylab("High Performance LINPACK, GFLOP/s")+
  theme(legend.position="bottom")+guides(color=guide_legend(nrow=2,byrow=TRUE))
ggsave("hpl2.png",width = 4, height = 4,dpi = 300)
```

### FFT

```{r results='asis', echo=FALSE, fig.width = 6, fig.height = 2}

# Averaged over all MPI process
# so report per core
s_fft <- "Fast Fourier Transform (FFTW) Floating-Point Performance"
fft <- hpcc %>% filter(metric == s_fft) %>%
        group_by(config,cores) %>%
        summarise(average=mean(value),stdev=sd(value),.groups = "drop_last") %>%
        ungroup()
# dput(unique(fft$config))
FFTrename <- list(
  "Ookami; cray,libsci,fftw-cray,mvapich"="Ookami, FFTW-Cray",
  "Ookami; gcc,armpl,mvapich"="Ookami, ARMPL",
  "Ookami; gcc,openblas,fftw-rd,mvapich"="Ookami, FFTW-Dolbeau",
  "Stampede2-SKX; icc,mkl,intel-mpi"="Stampede2-SKX, MKL"
)
fft$sys <- recode(fft$config,!!!FFTrename)
fft$sys <- factor(fft$sys,levels = rev(FFTrename))
fft$nodes <- as.integer(fft$cores/48)
fft$average <- fft$average / 1000
fft$stdev <- fft$stdev / 1000
fft$tflops <- 57.6 * fft$cores
fft$tflops[grepl("Stampede2",fft$sys)] <- 44.8 * fft$cores
fft$label <- paste0(round(fft$average,2)," (",
                      round(100*fft$average/fft$tflops,2),"%)")
# ookami: single core peak (57.6 GFLOP/s)
# stampede avx512 base 1.4 GHz turbo 2.0
# https://www.intel.com/content/dam/www/public/us/en/documents/specification-updates/xeon-scalable-spec-update.pdf
# freq*8(width)*2*(fma)*2(units)
# stampede peak=44.8 (64 at turbo)


ggplot(fft %>% filter(nodes==1), aes(x=sys, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
  geom_text(aes(label=label),hjust=-.2, vjust=0.5)+
        ylab("Fast Fourier Transform (FFT), GFLOP/s per node")+
        coord_flip()+ ylim(0,60)+
  theme(axis.title.y=element_blank(),
        axis.text.y = element_text(color="black",size=12))
```
```{r results='asis', echo=FALSE, fig.width = 4, fig.height = 4}
#hpl$sys <- factor(as.character(hpl$config),levels = c("Ookami, LibSci","Ookami, ARMPL","Ookami, OpenBLAS","Stampede2-SKX, MKL"))
#FFTrename
fft$sys2 <- factor(as.character(fft$sys),levels = c("Ookami, FFTW-Cray","Ookami, ARMPL","Ookami, FFTW-Dolbeau","Stampede2-SKX, MKL"))
fft_perf <- read.csv("perfect_scaling_fft.csv",sep=";",as.is = T)
fft_perf$sys2 <- factor(as.character(fft_perf$sys2),levels = c("Ookami, FFTW-Cray","Ookami, ARMPL","Ookami, FFTW-Dolbeau","Stampede2-SKX, MKL"))


ggplot(fft, aes(x=nodes, y=average, color=sys)) + geom_point() + geom_line() +
  geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=0.05) + labs(color="") +
  geom_line(data = fft_perf,mapping = aes(x=nodes, y=average, color=sys2), linetype = 2) +
  scale_x_continuous(trans='log2') +
  scale_y_continuous(trans='log10') +
  ylab("Fast Fourier Transform, GFLOP/s")+
  theme(legend.position="right")+
  theme(legend.position="bottom")+guides(color=guide_legend(nrow=2,byrow=TRUE))
ggsave("fft2.png",width = 4, height = 4,dpi = 300)
```

### STREAM

```{r results='asis', echo=FALSE, fig.width = 6, fig.height = 2}

# Averaged over all MPI process
# so report per core
s_stream <- "Average STREAM 'Triad' Memory Bandwidth"
stream <- hpcc %>% filter(metric == s_stream) %>%
        group_by(config,cores) %>%
        summarise(average=mean(value),stdev=sd(value),.groups = "drop_last") %>%
        ungroup()
# dput(unique(stream$config))
streamrename <- list(
  "Ookami; cray,libsci,fftw-cray,mvapich"="Ookami, cray, LibSci",
  "Ookami; gcc,armpl,mvapich"="Ookami, gcc, ARMPL",
  "Ookami; gcc,openblas,fftw-rd,mvapich"="Ookami, gcc, OpenBLAS",
  "Stampede2-SKX; icc,mkl,intel-mpi"="Stampede2-SKX, icc, MKL"
)
stream$sys <- recode(stream$config,!!!streamrename)
stream$sys <- factor(stream$sys,levels = rev(streamrename))
stream$nodes <- as.integer(stream$cores/48)
stream$average <- stream$cores * stream$average / 1024
stream$stdev <- stream$cores * stream$stdev / 1024
stream$tgbs <- 1024 * stream$nodes
stream$tgbs[grepl("Stampede2",stream$sys)] <- (21333.33/1024) * 12 * stream$nodes
stream$label <- paste0(round(stream$average,2)," (",
                      round(100*stream$average/stream$tgbs,2),"%)")
# ookami: single core peak (57.6 GFLOP/s)
# stampede avx512 base 1.4 GHz turbo 2.0
# https://www.intel.com/content/dam/www/public/us/en/documents/specification-updates/xeon-scalable-spec-update.pdf
# freq*8(width)*2*(fma)*2(units)
# stampede peak=44.8 (64 at turbo)


ggplot(stream %>% filter(nodes==1), aes(x=sys, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
  geom_text(aes(label=label),hjust=-.2, vjust=0.5)+
        ylab("STREAM 'Triad' Memory Bandwidth, GB/s per node")+
        coord_flip()+ #ylim(0,60)+
  theme(axis.title.y=element_blank(),
        axis.text.y = element_text(color="black",size=12))
```


## Overall Performance (That is per All MPI Processes)

```{r results='asis', echo=FALSE, fig.width = 11, fig.height = 6}
for(stat in stats_overall) {
    stat_units <- units$units[units$metric==stat]
    if(stat_units=="") {
        cap <- stat
    } else {
        cap <- paste0(stat, ", ", stat_units)
    }
    cat(paste0("<h3>",cap,"</h3>\n"))
    perf <- hpcc %>% filter(metric == stat) %>%
        group_by(config,cores) %>%
        summarise(average=mean(value),stdev=sd(value),.groups = "drop_last") %>%
        ungroup() %>% mutate(conf=paste(config,cores, sep = ", ")) %>%
        mutate(conf=factor(conf, levels = rev(conf)))
    print(ggplot(perf, aes(x=conf, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
        coord_flip()+ylab(cap))
    cat(kable(perf %>% select(-conf), caption = cap, digits = 2, "html") %>%
        kable_styling(full_width = F))
}
for(stat in stats_per_core) {
    stat_units <- units$units[units$metric==stat]
    if(stat_units=="") {
        cap <- stat
    } else {
        cap <- paste0(stat, ", ", stat_units)
    }
    cat(paste0("<h3>",cap,"</h3>\n"))
    perf <- hpcc %>% filter(metric == stat) %>%
        group_by(config,cores) %>%
        summarise(average=mean(value*cores),stdev=sd(value*cores),.groups = "drop_last") %>%
        ungroup() %>% mutate(conf=paste(config,cores, sep = ", ")) %>%
        mutate(conf=factor(conf, levels = rev(conf)))
    print(ggplot(perf, aes(x=conf, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
        coord_flip()+ylab(cap))
    cat(kable(perf %>% select(-conf), caption = cap, digits = 2, "html") %>%
        kable_styling(full_width = F))
}
```

### Performance per Core (that is MPI Process)

```{r results='asis', echo=FALSE, fig.width = 11, fig.height = 6}
for(stat in stats_overall) {
    stat_units <- units$units[units$metric==stat]
    if(stat_units=="") {
        cap <- stat
    } else {
        cap <- paste0(stat, ", ", stat_units)
    }
    cat(paste0("<h3>",cap,"</h3>\n"))
    perf <- hpcc %>% filter(metric == stat) %>%
        group_by(config,cores) %>%
        summarise(average=mean(value/cores),stdev=sd(value/cores),.groups = "drop_last") %>%
        ungroup() %>% mutate(conf=paste(config,cores, sep = ", ")) %>%
        mutate(conf=factor(conf, levels = rev(conf)))
    print(ggplot(perf, aes(x=conf, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
        coord_flip()+ylab(cap))

    cat(kable(perf %>% select(-conf), caption = cap, digits = 2, "html") %>%
        kable_styling(full_width = F))
}
for(stat in stats_per_core) {
    stat_units <- units$units[units$metric==stat]
    if(stat_units=="") {
        cap <- stat
    } else {
        cap <- paste0(stat, ", ", stat_units)
    }
    cat(paste0("<h3>",cap,"</h3>\n"))
    perf <- hpcc %>% filter(metric == stat) %>%
        group_by(config,cores) %>%
        summarise(average=mean(value),stdev=sd(value),.groups = "drop_last") %>%
        ungroup() %>% mutate(conf=paste(config,cores, sep = ", ")) %>%
        mutate(conf=factor(conf, levels = rev(conf)))
    print(ggplot(perf, aes(x=conf, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
        coord_flip()+ylab(cap))
    cat(kable(perf %>% select(-conf), caption = cap, digits = 2, "html") %>%
        kable_styling(full_width = F))
}
```



