---
title: "HPCC"
author: nikolays
date: 7/28/20
output:
  html_notebook:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(cowplot)
library(knitr)
library(kableExtra)
```

```{r include=FALSE}
# Read data
hpcc <- read.csv("data/hpcc.csv", stringsAsFactors=F) %>%
    select(-X) %>% filter(metric != "App:Version") %>%
    mutate(
        value=as.numeric(value),
        exe_type=factor(exe_type),
        problem_size=factor(problem_size),
        metric_type=factor(metric_type),
        metric=factor(metric),
        units=factor(units),
        resource=factor(resource, c(
            "Koinu (CPU ARM ThunderX2 32(128) cores x2)",
            "Stampede2 SKX (CPU Intel Xeon Platinum 8160 24(48) cores x2)",
            "Stampede2 KNL (CPU Intel Xeon Phi 7250 68(272) cores x2)",
            "Comet (CPU Intel Xeon E5-2680v3 12 cores x2, Haswell)",
            "Bridges (Intel E5-2695 v3 14 cores x2, Haswell)")),
        exe_type=factor(exe_type, c(
            "openmpi/sysblas/intfft",
            "openmpi/openblas/intfft",
            "openmpi/armpl/intfft",
            "impi/mkl", "mvapich2/mkl"))
    )
#dput(unique(hpcc$exe_type))
#head(hpcc)
```

```{r include=FALSE}
# statistics we are interested in
#dput(unique(hpcc$metric[hpcc$metric_type=="statistic"]))
stats_overall <- c(
    "High Performance LINPACK Floating-Point Performance",
    "Fast Fourier Transform (FFTW) Floating-Point Performance",
    "Parallel Matrix Transpose (PTRANS)",
    "MPI Random Access"
)
stats_per_core <- c(
    "Average Double-Precision General Matrix Multiplication (DGEMM) Floating-Point Performance",
    "Average STREAM 'Triad' Memory Bandwidth",
    "Average STREAM 'Add' Memory Bandwidth",
    "Average STREAM 'Copy' Memory Bandwidth",
    "Average STREAM 'Scale' Memory Bandwidth"
)
units <- hpcc %>% group_by(metric) %>% summarise(units=as.character(first(units))) %>%
    ungroup()
units$units[is.na(units$units)]<-""
```

Everything is executed on single node, average of 10 runs.

# Metrics

Some of reported HPCC metrics:

 * Average Double-Precision General Matrix Multiplication (DGEMM) Floating-Point Performance
   + Embarrassingly parallel, Averaged over all MPI process, MFLOP per Second per MPI process
   + (There is also serial metric; measured but not analysed)
 * High Performance LINPACK Floating-Point Performance
   + Parallel, overall MFLOP per Second
 * Fast Fourier Transform (FFTW) Floating-Point Performance
   + Parallel, MFLOP per Second
   + (There are also serial and embarrassingly parallel metrics; measured but not analysed)
 * Parallel Matrix Transpose (PTRANS)
   + Parallel, overall MByte per Second
 * MPI Random Access
   + Parallel, overall MUpdate per Second
   + (There are also serial and embarrassingly parallel metrics; measured but not analysed)
 * Average STREAM 'Triad'/ 'Add' / 'Copy' / 'Scale' Memory Bandwidth
   + Embarrassingly parallel, Averaged over all MPI process, MByte per Second
   + (There is also serial metric; measured but not analysed)

# Results
## Overall Performance (That is per All MPI Processes)

```{r results='asis', echo=FALSE, fig.width = 11, fig.height = 6}
for(stat in stats_overall) {
    stat_units <- units$units[units$metric==stat]
    if(stat_units=="") {
        cap <- stat
    } else {
        cap <- paste0(stat, ", ", stat_units)
    }
    cat(paste0("<h3>",cap,"</h3>\n"))
    perf <- hpcc %>% filter(metric == stat) %>%
        group_by(resource,exe_type,cpus) %>%
        summarise(average=mean(value),stdev=sd(value)) %>%
        ungroup() %>% mutate(conf=paste(resource,exe_type,cpus, sep = ", ")) %>%
        mutate(conf=factor(conf, levels = rev(conf)))
    print(ggplot(perf, aes(x=conf, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
        coord_flip()+ylab(cap))
    print(kable(perf %>% select(-conf), caption = cap, digits = 2, "html") %>%
        kable_styling(full_width = F))
}
for(stat in stats_per_core) {
    stat_units <- units$units[units$metric==stat]
    if(stat_units=="") {
        cap <- stat
    } else {
        cap <- paste0(stat, ", ", stat_units)
    }
    cat(paste0("<h3>",cap,"</h3>\n"))
    perf <- hpcc %>% filter(metric == stat) %>%
        group_by(resource,exe_type,cpus) %>%
        summarise(average=mean(value*cpus),stdev=sd(value*cpus)) %>%
        ungroup() %>% mutate(conf=paste(resource,exe_type,cpus, sep = ", ")) %>%
        mutate(conf=factor(conf, levels = rev(conf)))
    print(ggplot(perf, aes(x=conf, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
        coord_flip()+ylab(cap))
    print(kable(perf %>% select(-conf), caption = cap, digits = 2, "html") %>%
        kable_styling(full_width = F))
}
```

### Performance per Core (that is MPI Process)

```{r results='asis', echo=FALSE}
for(stat in stats_overall) {
    stat_units <- units$units[units$metric==stat]
    if(stat_units=="") {
        cap <- stat
    } else {
        cap <- paste0(stat, ", ", stat_units)
    }
    cat(paste0("<h3>",cap,"</h3>\n"))
    perf <- hpcc %>% filter(metric == stat) %>%
        group_by(resource,exe_type,cpus) %>%
        summarise(average=mean(value/cpus),stdev=sd(value/cpus)) %>%
        ungroup() %>% mutate(conf=paste(resource,exe_type,cpus, sep = ", ")) %>%
        mutate(conf=factor(conf, levels = rev(conf)))
    print(ggplot(perf, aes(x=conf, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
        coord_flip()+ylab(cap))
    print(kable(perf %>% select(-conf), caption = cap, digits = 2, "html") %>%
        kable_styling(full_width = F))
}
for(stat in stats_per_core) {
    stat_units <- units$units[units$metric==stat]
    if(stat_units=="") {
        cap <- stat
    } else {
        cap <- paste0(stat, ", ", stat_units)
    }
    cat(paste0("<h3>",cap,"</h3>\n"))
    perf <- hpcc %>% filter(metric == stat) %>%
        group_by(resource,exe_type,cpus) %>%
        summarise(average=mean(value),stdev=sd(value)) %>%
        ungroup() %>% mutate(conf=paste(resource,exe_type,cpus, sep = ", ")) %>%
        mutate(conf=factor(conf, levels = rev(conf)))
    print(ggplot(perf, aes(x=conf, y=average)) +
        geom_bar(stat="identity", fill="royalblue", color="royalblue4") +
        geom_errorbar(aes(ymin=average-stdev, ymax=average+stdev), width=.2)+
        coord_flip()+ylab(cap))
    print(kable(perf %>% select(-conf), caption = cap, digits = 2, "html") %>%
        kable_styling(full_width = F))
}
```
